Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-02-24 Manuscript_TIFS/manuscript_TIFS.tex
update: experiment部分的攻击类型和threat model
subfigure字体大小修改（未完成

\begin{figure*}[!htp]
  \centering
    \subfloat[\scriptsize MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
    \subfloat[\scriptsize MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
    \subfloat[\scriptsize MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
    \subfloat[\scriptsize MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}

    \subfloat[\scriptsize Fashion-MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
    \subfloat[\scriptsize Fashion-MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
    \subfloat[\scriptsize Fashion-MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
    \subfloat[\scriptsize Fashion-MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}

    \subfloat[\scriptsize CIFAR-10 {$q=0.1$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
    \subfloat[\scriptsize CIFAR-10 {$q=0.2$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
    \subfloat[\scriptsize CIFAR-10 {$q=0.5$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
    \subfloat[\scriptsize CIFAR-10 {$q=0.8$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on MNIST on different imbalance degrees.}
  \label{fig_exp_reputation}
  \vspace{0.2in}
\end{figure*}

@@

  \begin{figure*}[!htp]
    \centering
    \subfloat[\scriptsize Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_random_bar.pdf}}
    \subfloat[\scriptsize Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_untargeted_bar.pdf}}
    \hfill
    \subfloat[\scriptsize Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_random_bar.pdf}}
    \subfloat[\scriptsize Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_untargeted_bar.pdf}}
    \caption{Experiments results under different Byzantine fractions and different imbalance degrees.}
    \label{fig_exp_extreme}
  \end{figure*}

  \begin{figure*}[!htp]
    \centering
    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Imbalance Degrees under Random Attack.}
    \label{fig_table_imbalances_random}
  \end{figure*}

  \begin{figure*}[!htp]
    \centering
    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Byzantine Fractions under Random Attack.}
    \label{fig_table_byzantines_random}
  \end{figure*}

  \par Each client has 1,000 samples taken from the training dataset. Among the samples, 800 of them are used as training datasets, while another 200 are taken as test datasets. And the server has 10000 testing examples from the testing dataset. 
  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish(weight) against two Byzantine denial-of-service attacks:
  \begin{itemize}
    \item Untargeted Byzantine Attacks: For each Byzantine client, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish(weight). The attack is known as the Label-flipping attack. 
    \item Random Byzantine Attacks: For each Byzantine client, it mislabels the labels by returning a randomly chosen result.
    \end{itemize}

@@

  \begin{figure*}[!htp]
    \centering
    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Imbalance Degrees under Untargeted Attack.}
    \label{fig_table_imbalances_untargeted}
  \end{figure*}

  \begin{figure*}[!htp]
    \centering
    \subfloat[\scriptsize MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
    \subfloat[\scriptsize Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
    \subfloat[\scriptsize CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Byzantine Fractions under Untargeted Attack.}
    \label{fig_table_byzantines_untargeted}
  \end{figure*}

>>>>

\begin{figure*}[!htp]

  \centering
    \subfloat[MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_1.pdf}}
    \subfloat[MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_2.pdf}}
    \subfloat[MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_5.pdf}}
    \subfloat[MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_mnist_imbalance_9.pdf}}

    \subfloat[Fashion-MNIST $q=0.1$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_1.pdf}}
    \subfloat[Fashion-MNIST $q=0.2$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_2.pdf}}
    \subfloat[Fashion-MNIST $q=0.5$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_5.pdf}}
    \subfloat[Fashion-MNIST $q=0.8$]{\includegraphics[width=0.245\textwidth]{figures/rep_fashion_imbalance_9.pdf}}

    \subfloat[CIFAR-10 {$q=0.1$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_1.pdf}}
    \subfloat[CIFAR-10 {$q=0.2$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_2.pdf}}
    \subfloat[CIFAR-10 {$q=0.5$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_5.pdf}}
    \subfloat[CIFAR-10 {$q=0.8$}]{\includegraphics[width=0.245\textwidth]{figures/rep_cifar_imbalance_9.pdf}}
  \\
  \caption{Reputation values of experiments on MNIST on different imbalance degrees.}
  \label{fig_exp_reputation}
  \vspace{0.2in}
\end{figure*}

@@

  \begin{figure*}[!htp]
    \centering
    \subfloat[Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_random_bar.pdf}}
    \subfloat[Byzantine Fraction 0.9 \& Imbalance Degree 0.2 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_byzantines_untargeted_bar.pdf}}
    \hfill
    \subfloat[Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Random Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_random_bar.pdf}}
    \subfloat[Byzantine Fraction 0.5 \& Imbalance Degree 0.8 \& Untargeted Attack]{\includegraphics[width=0.48\textwidth]{figures/bar_imbalances_untargeted_bar.pdf}}
    \caption{Experiments results under different Byzantine fractions and different imbalance degrees.}
    \label{fig_exp_extreme}
  \end{figure*}

  \begin{figure*}[!htp]
    \centering
    \subfloat[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_MNIST.pdf}}
    \subfloat[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Fashion-MNIST.pdf}}
    \subfloat[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_imbalances_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Imbalance Degrees under Random Attack.}
    \label{fig_table_imbalances_random}
  \end{figure*}

  \begin{figure*}[!htp]
    \centering
    \subfloat[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_MNIST.pdf}}
    \subfloat[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Fashion-MNIST.pdf}}
    \subfloat[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_random_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Byzantine Fractions under Random Attack.}
    \label{fig_table_byzantines_random}
  \end{figure*}

  \par Each client has 1,000 samples taken from the training dataset. Among the samples, 800 of them are used as training datasets, while another 200 are taken as test datasets. And the server has 10000 testing examples from the testing dataset. 
  \subsubsection{\textit{Evaluated Byzantine Attacks}} We evaluate our FLPhish(weight) against two Byzantine denial-of-service attacks mentioned in Section III.B:
  \begin{itemize}
    \item Untargeted Byzantine Attacks: For each Byzantine client, it mislabels the data $l$ to $(l-1)\ mod\ M$ to launch the attacks against FLPhish(weight). The attack is known as the Label-flipping attack. 
    \item Random Byzantine Attacks: For each Byzantine client, it mislabels the labels by returning a randomly chosen result.
    \end{itemize}

@@

  \begin{figure*}[!htp]
    \centering
    \subfloat[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_MNIST.pdf}}
    \subfloat[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Fashion-MNIST.pdf}}
    \subfloat[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_imbalances_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Imbalance Degrees under Untargeted Attack.}
    \label{fig_table_imbalances_untargeted}
  \end{figure*}

  \begin{figure*}[!htp]
    \centering
    \subfloat[MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_MNIST.pdf}}
    \subfloat[Fashion-MNIST]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Fashion-MNIST.pdf}}
    \subfloat[CIFAR-10]{\includegraphics[width=0.325\textwidth]{figures/table_untargeted_byzantines_Cifar-10.pdf}}
    \\
    \caption{Accuracy values on Different Byzantine Fractions under Untargeted Attack.}
    \label{fig_table_byzantines_untargeted}
  \end{figure*}
